---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# hw07-lsloboda

## Overview
**This repo contains the files relevant to STAT 545 Homework 07.**
  The homework file is located [here](https://github.com/STAT545-UBC-students/hw07-lsloboda/blob/master/hw07-lsloboda.md).

## Purpose

|    **Item**                                     | **Status** |
  |-------------------------------------------------|------------|
  | *Add a function to the R powers package:*                   |
  | *Define & export min. 1 new function*    | :thumbsup: |
  | *Give arguments sensible defaults*    | :thumbsup: |
  | *Update the documentation*    | :thumbsup: |
  | *Perform min. 3 unit tests for common cases*    | :thumbsup: |
  | *Pass 'check' without errors*    | :thumbsup: |
  | *Update the README and vignette*    | :thumbsup: |
  | *Modify the instructions to tell someone how to install the package*    | :thumbsup: |

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Build Status](https://travis-ci.org/vincenzocoia/powers.svg?branch=master)](https://travis-ci.org/vincenzocoia/powers)

__Note__: This R package is not mean to be "serious". It's just for teaching purposes. 

# powers

This is an R package that gives `sqrt()` friends by providing other power functions.

## Installation

You can install powers from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
#devtools::install_github("lsloboda/powers")
```

## Example

See the vignette for more extensive use, but here's an example of the boxcox function:

```{r example}
#powers::boxcox(1:10, 2)
```

## For Developers

(Again, I don't actually intend for anyone to develop this silly package, but if I did, here's what I'd write.)

Use the internal `pow` function as the machinery for the front-end functions such as `square`, `cube`, `reciprocal`, and `boxcox`. 
